---
title: "DOSCHEDA report"
output: html_document
params:
  reps: NA
  chans: NA
  data: NA
  data2: NA
  channel: NA
  avthrsli: NA
  pvalsli: NA
  indexmat: NA
  RSu: NA
  finNam: NA
  datype: NA
  sigmodin: NA
  concen: NA
  sigPred: NA
  vennip: NA
  kin: NA
---
  upVenn: NA
 
```{r packageload, echo = FALSE, warning=FALSE}
 
library(hexbin)
library(limma)
```
This is a summary of the data processing and plots created in the DOSCHEDA shiny app.
   
 
Number of Channels | Number of Replicates | Input Type | Sigmoidal Fit
---|---|---|---
`r params$chans`|`r params$reps` | `r params$datype` | `r params$sigmodin`
 
 
```{r reptest,echo = FALSE}
   reptest <- ifelse(params$reps > 1,TRUE,FALSE) 
```
**Figure 1: Box plot of Data Columns**
 
```{r boxplo, echo=FALSE,fig.cap= "Boxplot per column in data"}
panel.shadeNtext <- function (x, y, corr = NULL, col.regions, ...)
{
  if (is.null(corr))
    corr <- cor(x, y, use = "pair")
  ncol <- 14
  pal <- col.regions(ncol)
  col.ind <- as.numeric(cut(corr, breaks = seq(from = -1, to = 1,
                                               length = ncol + 1), include.lowest = TRUE))
  usr <- par("usr")
  rect(usr[1], usr[3], usr[2], usr[4], col = pal[col.ind],
       border = NA)
  box(col = "lightgray")
  on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- formatC(corr, digits = 2, format = "f")
  cex.cor <- .8/strwidth("-X.xx")
  text(0.5, 0.5, r, cex = cex.cor)
}
 

vec<- params$channel
    vec<- length(vec)
       palette.bar <- rep(terrain.colors(params$reps),each = ifelse(params$datype != 'intensity',params$chans,params$chans - 1 ) )

    data.merged1<- params$data
    boxplot(data.merged1[,1:vec], col=palette.bar,las=2, cex.axis=0.6, main=c("Box Plots"),
            ylab=c("Log2(ratios)"))
   
        legend("topright",legend = paste("rep",1:params$reps,sep = ' '), fill = terrain.colors(params$reps))

 
```
 
**Description:**
 
Here we should observe the means centered at approximately zero across all channels and replicates. This is meant as a preliminary plot, potentially hilighting issues with the data.
 
 
 
**Figure 2: Ranked plot of proteins FC and Density plot of Data Columns**
 
```{r scatt, echo = FALSE}

    
    vec<- params$channel
    pal <- rainbow(length(vec))
    missing_val <- 0
    if(params$datype == 'intensity' & params$reps == 1 ){
     leg.nam <- paste0('rep1_C',0:(params$chans -2))
    }else{
        leg.nam <- params$finNam
   }
    par(mfrow = c(1,2))   
    plot(x=rank(data.merged1[,1]),y=data.merged1[,1], cex.axis=0.6,
         main=c(paste("N. of Missing val. ",missing_val ,
                      " \n Change Distribution after LOESS",sep="")),
         col=pal[1], ylab=c("Log2(ratios)"), xlab = c("Proteins"))
    if(length(vec) > 1){
      for(i in 2:length(vec)){
        points(x=rank(data.merged1[,i]),y=data.merged1[,i], cex.axis=0.6, main=c(""),col=pal[i])
      }
    }
   legend("topleft", legend = leg.nam, fill = pal)
    
    
    plot(density(x=data.merged1[,1]),col= pal[1], main=c(" Density after LOESS"), ylim = c(0,5 ))
   
    
    if(length(vec) > 1){
      for(i in 2:length(vec)){
        lines(density(x=data.merged1[,i]), col=pal[i], main = c(""))
      }
    }
 legend("topleft", legend = leg.nam, fill = pal)
```
 
**Description:**
 
 
In these both plots in Figure 2 we expect the channels to more or less overlay. The Density plots should have a bell shaped distributions and be approximately centred at zero. Similalry to Fig. 1, these are intended to be preliminary plots.
 
 
**Figure 3: Venn Diagram** 

```{r vennplo, echo = FALSE}
kinome1<- params$kin
kinome<-as.vector(toupper(kinome1$new.Symbol))

if((params$vennip) == TRUE){

      upload <- params$upVenn
      upload<- as.vector(toupper(upload))
      data.merged <- params$data

      proteome<-as.vector(toupper(data.merged$GeneID))
      universe <- unique(c(kinome,proteome,upload))

      count<- matrix(0, ncol = 3 , nrow = length(universe))
      colnames(count) <- c("kinome",'proteome','upload')

      for(i in 1:length(universe)){
        count[i,1]<- universe[i] %in% kinome
        count[i,2]<- universe[i] %in% proteome
        count[i,3]<- universe[i] %in% upload
      }

      vennDiagram(vennCounts(count), circle.col = c("blue","red","green"), cex = 1,lwd = 2)


    }else{
      
      data.merged <- params$data
      
      proteome<-as.vector(toupper(data.merged$GeneID))
      universe <- unique(c(kinome,proteome))
      # Generate a matrix, with the sets in columns and possible letters on rows
      Counts <- matrix(0, nrow=length(universe), ncol=2)
      # Populate the said matrix
      for (i in 1:length(universe)) {
        Counts[i,1] <- universe[i] %in% kinome
        Counts[i,2] <- universe[i] %in% proteome
        #Counts[i,3] <- universe[i] %in% Metacore
        #Counts[i,3] <- universe[i] %in% EXOCYTOSIS
        
      }
      
      colnames(Counts) <- c("Kinome","Proteome")
      cols<-c("Red", "Blue")
      
      #### VENN
      
      vennDiagram(vennCounts(Counts), circle.col=cols,
                  cex=1, #title size
                  lwd=2 #circle line size
      )
     }

```
 
**Figure 3: Mean vs standard deviation plot**
 
```{r meansd, echo = FALSE}
 
meanSdPlot(as.matrix(data.merged1[,1:length(vec)]))
 
```
 
**Description:**
 
Figure 3 plots the ranked row means and standard deviations and is intended to give a visual indication whether there is dependence of the variance on the mean. The red line is a running median estimator with window-width at 10%. If this red line is approximately horizontal, this indicates no variance-mean dependence.
 
 
**Figure 4: Mean vs SD plots for each Protein.**
 
```{r tmdplo, echo = FALSE,eval = reptest}
    rSu<- params$RSu
    nrow(params$indexmat)
     for(i in 1:nrow(params$indexmat)){
     
    minxy <- min(c(min(rSu[,params$indexmat[i,5]]),min(rSu[,params$indexmat[i,6]])))
    maxxy <- max(c(max(rSu[,params$indexmat[i,5]]),max(rSu[,params$indexmat[i,6]])))
   
    print(tmd(
      xyplot(rSu[,params$indexmat[i,5]] ~ rSu[,params$indexmat[i,6]]), main=params$indexmat[i,1],xlim = c(minxy,maxxy),
      ylim = c(minxy,maxxy),
      panel=function(x, y, ...) {
        panel.xyplot(x, y, ...);
        ltext(x=x, y=y, labels=rSu$GeneID, pch=c(13,3,16), cex=0.5, lwd=2, pos=1, offset=1, pch = 19)
      }))
   
     }
 
```
 
**Description:**
 
Figure 4 are the plots of the mean and the standard devaiation between the the replicates. Here we look for the majority of proteins to be within a cloud and that this cloud is more or less horizontal. These plots complement Figure 3.
 
 
 
**Figure 5: Pearson Correlation between Conditions**
 
```{r corrgrm, echo = FALSE }
 
    index1 <- params$channel
    index1<- length(index1)
    cmat <-cor(params$RSu[,1:index1],use="pairwise", method = "pearson")
    corrgram(cmat, order=TRUE, lower.panel=panel.shadeNtext,
             upper.panel=panel.pie, text.panel=panel.txt,
             main="Corrgram Plots" )
 
```
 
**Description:**
 
Figure 5 shows the pearson correlations between all the different channels. We expect none of the channels to be anti-correlated, that is to have a correlation coeffcient less than 0.
 
 
 
**Figure 6: Principal-Component Analysis of Data columns**
```{r pca , echo = FALSE}
 
if( params$datype == 'intensity'){
     if(params$reps == 1){
       nchan<- params$chans - 1
     }
  # else {
  #      nchan<- params$chans - 2
  #      
  #    }
    }else{
     
     nchan<- params$chans
    }
   
 if( params$datype == 'intensity'){
      
      nchan<- params$chans - 1
      
    }else{
      
      nchan<- params$chans
    }
    
    su <- params$RSu
    reps <- params$reps
    index <- params$channel

    pca <- prcomp(su[,1:length(index)], scale=F)
    
    DTA<-data.frame( as.numeric(t(su[,1:length(index)])%*%pca$x[,1]),
                     as.numeric(t(su[,1:length(index)])%*%pca$x[,2]))
    

    p<-ggplot(DTA, aes(x=DTA$as.numeric.t.su...1.length.index........pca.x...1..,
                       y=DTA$as.numeric.t.su...1.length.index........pca.x...2..))
    # nchan/3 -> 3 if 3 replicates 2 if 2 reps and son on
        shapeval <- c(16:20,7:12)
    p <- p + geom_point(aes(colour = factor(rep(1:params$reps,each = (nchan)),labels = paste("Rep",1:params$reps))[index],
                            shape = factor(rep(1:nchan,params$reps),labels = c(paste("C",0:(nchan-1),sep = "")))[index] ), size = 5 ) + scale_shape_manual(values=shapeval[1:nchan]) + labs(x = "PC1", y = "PC2", title="PCA") + labs(color = "Replicates", shape="Concentration")
    
    p

```
 
**Description:**
 
Plot of the data as described the two highest principal components. This plot is mean to give an idea if any data points are vastly 'out of place' and is best used in conjungtion with the other plots provided, not on its own.
 
 
**Figure 7: Replicate vs Replicate plots for each Channel.**
 
```{r repvsrep, echo = FALSE,eval = reptest}
 
 
 
   
for( i in 1:nrow(params$indexmat)){
 
  val = max(c(max(data.merged1[,params$indexmat[i,5]],na.rm = TRUE),max(data.merged1[,params$indexmat[i,6]],na.rm = TRUE)))
   
    plot(x=data.merged1[,params$indexmat[i,5]],y=data.merged1[,params$indexmat[i,6]], xlim=c(0,val +0.2), col="green" , ylim=c(0,val+0.2),
         cex.axis=1.2, main=paste("LogFC-LogFC Plot:", params$indexmat[i,1]),
         xlab=paste("rep",params$indexmat[i,3]),  ylab=paste("rep",params$indexmat[i,4]))
    text(data.merged1[,params$indexmat[i,5]], data.merged1[,params$indexmat[i,6]], labels=data.merged1$GeneID, cex= 0.7,pos=4)
    lines(x = c(0,val), y = c(0,val),col="red")
}
 
 
 
```
 
**Description:**
 
These plots in figure 7 are some of the most important of this report. Here we should be able to identify targets and potential off-targets, these being the points which have high fold change in both replicates and are close to the the red line which is the x = y line.
 
 
```{r shwt, echo=FALSE}
if(params$sigmodin == 'sigmoid'){
  show_text <- TRUE
} else{
  
  show_text <- FALSE
}
```
## Linear Model
 
These plots are relevant if you have decided to use a linear model on the data.
 
**Figure 8: Distribution of p-values of model coefficients**
 
```{r pvals, echo = FALSE,eval = !show_text}
 
data.merged2 <- params$data2
    m0 <- ggplot(data.merged2, aes(x=data.merged2$P.Value))
    m0<-m0 + geom_histogram(aes(fill = ..count..),binwidth = 0.01) +
      scale_fill_gradient("Count", low = "green", high = "red")+
      xlab("P.val slope")
    
    
    m1 <- ggplot(data.merged2, aes(x=data.merged2$P.Value.x))
    m1<- m1 + geom_histogram(aes(fill = ..count..),binwidth = 0.01) +
      scale_fill_gradient("Count", low = "green", high = "red")+
      xlab("Pval intercept")
   
    m2 <- ggplot(data.merged2, aes(x=data.merged2$P.Value.y))
    m2 <- m2 + geom_histogram(aes(fill = ..count..),binwidth = 0.01) +
      scale_fill_gradient("Count", low = "green", high = "red")+
      xlab("Pval quadratic")
   
    grid.arrange(m0,m1,m2)
 
```
 
**Description:**
 
We expect there to be at least some significant (p-value < 0.05) pvalues for each coefficient. Usually the most interesting proteins will be those with significant intercept and / or significant slope. The points which have quadratic coefficient indicate that the abundances are quantified more in a middle concentration, we deem this as strange behaviour. 
 
 
**Figure 9: Volcano plots of model coefficients**
 
```{r volslop, echo = FALSE,eval = !show_text}
 
    res<- data.merged2
    # avgthr=0.2 #sign threshold for the averege fold change 0.3(log2)  is 1.3 FC
   
    par(mar=c(5,5,5,10), xpd=TRUE)
    # Make a basic volcano plot
    with(res, plot(res$AveExpr.x, -log10(res$P.Value), pch=20, main="Volcano plot (slope pval )",
                   xlab=c("Log2_AvgFC"),ylab=c("-Log10(Pval)"),
                   xlim=c(-abs(max(res$AveExpr.x)+1),abs(max(res$AveExpr.x)+1))))
   
    # Add colored points: red if padj<0.05, orange of log2FC>1, green if both)
    s=subset(res, P.Value< params$pvalsli )
    with(s, points(s$AveExpr.x, -log10(s$P.Value), pch=20, col="red"))
   
    s=subset(res, abs(res$AveExpr.x)>params$avthrsli)
    with(s, points(s$AveExpr.x, -log10(s$P.Value), pch=20, col="orange"))
   
    s=subset(res, P.Value< params$pvalsli & abs(res$AveExpr.x)>params$avthrsli)
    with(s, points(s$AveExpr.x, -log10(s$P.Value), pch=20, col="green"))
   
    # Label points with the textxy function from the calibrate plot
    s=subset(res, P.Value< params$pvalsli & abs(res$AveExpr.x)>params$avthrsli)
    with(s, textxy( s$AveExpr.x, -log10(s$P.Value),  labs=s$GeneID, cex=.7)
    )
        legend("bottomleft", title="Legend",cex = 0.7,
           c("Not significant",
             paste("P.Value",params$pvalsli, sep = " "), #red
             paste("AvgFC >", params$avthrsli, sep=""), #orange,
             paste("P.Value", params$pvalsli,"& AvgFC >", params$avthrsli, sep="") #green
           ),
           col=c("black","red","orange","green"),
           horiz=F, pch=c(19))
    # legend("topright", inset=c(-0.4,0.1), title="Legend",cex = 0.7,
    #        c("Not significant",
    #          "P.Value<.05", #red
    #          paste("AvgFC >", params$avthrsli, sep=""), #orange,
    #          paste("P.Value<.05 & AvgFC >", params$avthrssli, sep="") #green
    #        ),
    #        col=c("black","red","orange","green"),
    #        horiz=F, pch=c(19))
 
```
 
```{r volo, echo = FALSE,eval = !show_text}
 
res<- data.merged2
    # avgthr=0.2 #sign threshold for the averege fold change 0.3(log2)  is 1.3 FC
   
    par(mar=c(5,5,5,10), xpd=TRUE)
    # Make a basic volcano plot
    with(res, plot(res$AveExpr.x, -log10(res$P.Value.x), pch=20, main="Volcano plot (Intercept pval )",xlab=c("Log2_AvgFC"),ylab=c("-Log10(Pval)"), xlim=c(-abs(max(res$AveExpr.x)+1),abs(max(res$AveExpr.x)+1))))
   
    # Add colored points: red if padj<0.05, orange of log2FC>1, green if both)
    s=subset(res, P.Value.x<params$pvalsli )
    with(s, points(s$AveExpr.x, -log10(s$P.Value.x), pch=20, col="red"))
   
    s=subset(res, abs(res$AveExpr.x)> params$avthrsli)
    with(s, points(s$AveExpr.x, -log10(s$P.Value.x), pch=20, col="orange"))
   
    s=subset(res, P.Value.x< params$pvalsli & abs(res$AveExpr.x)> params$avthrsli)
    with(s, points(s$AveExpr.x, -log10(s$P.Value.x), pch=20, col="green"))
   
    # Label points with the textxy function from the calibrate plot
    s=subset(res, P.Value.x< params$pvalsli & abs(res$AveExpr.x)>params$avthrsli)
    with(s, textxy( s$AveExpr.x, -log10(s$P.Value.x),  labs=s$GeneID.x, cex=.7)
    )
            legend("bottomleft", title="Legend",cex = 0.7,
           c("Not significant",
             paste("P.Value",params$pvalsli, sep = " "), #red
             paste("AvgFC >", params$avthrsli, sep=""), #orange,
             paste("P.Value", params$pvalsli,"& AvgFC >", params$avthrsli, sep="") #green
           ),
           col=c("black","red","orange","green"),
           horiz=F, pch=c(19))
    # legend("topright", inset=c(-0.4,0.1), title="Legend",cex = 0.7,
    #        c("Not significant",
    #          "P.Value<.05", #red
    #          paste("AvgFC >", params$avthrsli, sep=""), #orange,
    #          paste("P.Value<.05 & AvgFC >", params$avthrsli, sep="") #green
    #        ),
    #        col=c("black","red","orange","green"),
    #        horiz=F, pch=c(19))
  
 
```
 
```{r volslo, echo = FALSE,eval = !show_text}
 
res<- data.merged2
    # avgthr=0.2 #sign threshold for the averege fold change 0.3(log2)  is 1.3 FC
   
    par(mar=c(5,5,5,10), xpd=TRUE)
    # Make a basic volcano plot
    with(res, plot(res$AveExpr.x, -log10(res$P.Value.y), pch=20, main="Volcano plot (Quadratic pval )",xlab=c("Log2_AvgFC"),ylab=c("-Log10(Pval)"), xlim=c(-abs(max(res$AveExpr.x)+1),abs(max(res$AveExpr.x)+1))))
   
    # Add colored points: red if padj<0.05, orange of log2FC>1, green if both)
    s=subset(res, P.Value.y<params$pvalsli )
    with(s, points(s$AveExpr.x, -log10(s$P.Value.y), pch=20, col="red"))
   
    s=subset(res, abs(res$AveExpr.x)>params$avthrsli)
    with(s, points(s$AveExpr.x, -log10(s$P.Value.y), pch=20, col="orange"))
   
    s=subset(res, P.Value.y<params$pvalsli & abs(res$AveExpr.x)>params$avthrsli)
    with(s, points(s$AveExpr.x, -log10(s$P.Value.y), pch=20, col="green"))
   
    # Label points with the textxy function from the calibrate plot
    s=subset(res, P.Value.y<params$pvalsli & abs(res$AveExpr.x)>params$avthrsli)
    with(s, textxy( s$AveExpr.x, -log10(s$P.Value.y),  labs=s$GeneID.x, cex=.7)
    )
            legend("bottomleft", title="Legend",cex = 0.7,
           c("Not significant",
             paste("P.Value",params$pvalsli, sep = " "), #red
             paste("AvgFC >", params$avthrsli, sep=""), #orange,
             paste("P.Value", params$pvalsli,"& AvgFC >", params$avthrsli, sep="") #green
           ),
           col=c("black","red","orange","green"),
           horiz=F, pch=c(19))
    # legend("topright", inset=c(-0.4,0.1), title="Legend",cex = 0.7,
    #        c("Not significant",
    #          "P.Value<.05", #red
    #          paste("AvgFC >", params$avthrsli, sep=""), #orange,
    #          paste("P.Value<.05 & AvgFC >", params$avthrsli, sep="") #green
    #        ),
    #        col=c("black","red","orange","green"),
    #        horiz=F, pch=c(19))
   
    
 
```
 
**Description:**
 
These are the volcano plots for the different coefficients for the linear fit
 
```{r heatmp, echo = FALSE, eval = FALSE}
 
    vec <- params$channel
    vec <- length(vec)
    su1 <- su[,1:vec]
    vec.nam <- params$finNam
    vec.nam <- vec.nam[params$channel]
    # nchan <- nchans()
    # index<- channels()
    # data_merged_Pvals<-data.frame(su[,index],
    #                               Accession=su$Accession,GeneID=su$GeneID)
    # #data_merged_Pvals<-data_merged_Pvals[GeneID=="NA", GeneID := Accession] substituting NA with Accession
    #
    
     d3heatmap(su1, Colv = FALSE,labRow = as.character(make.names(su$GeneID.x,unique = TRUE)))
    # m<- heatmaply(su,Colv= FALSE,
    #               labRow =  as.character(make.names(su$GeneID.x,unique = TRUE))) %>% layout(margin = list(l = 70, b = 70))
 
```

# Sigmoidal ... 

```{r sigmoidsetup,echo = FALSE}
shape_for_ggplot_pred<-function(df_ordered,conc,pred.names){
  cols_to_keep_pred<-c(pred.names,"GeneID","Accession")
  
  forggplot_pred<-vector(mode = "list",length = length(df_ordered$GeneID))
  
  for(i in 1:length(df_ordered$GeneID)){
    tmp_pred<-df_ordered[,cols_to_keep_pred]
    forggplot_pred[[i]]<-melt(tmp_pred[i,], id = c("GeneID", "Accession"), na.rm = TRUE)
  }
  
  forggplot_pred_1<-do.call(rbind, forggplot_pred)
  forggplot_pred_1<-data.frame(forggplot_pred_1,"x"=conc)
  #return(forggplot_pred_1)
}

shape_for_ggplot_perc<-function(df_ordered,conc,finalNames){
  cols_to_keep_perc<-c(finalNames, "GeneID","Accession")
  
  forggplot_perc<- vector(mode = "list",length = length(df_ordered$GeneID))
  for(i in 1:length(df_ordered$GeneID)){
    tmp_perc<-df_ordered[,cols_to_keep_perc]
    forggplot_perc[[i]]<-melt(tmp_perc[i,], id = c("GeneID", "Accession"), na.rm = TRUE)
  }
  
  forggplot_perc_1<-do.call(rbind, forggplot_perc)
  forggplot_perc_1<-data.frame(forggplot_perc_1,"x"=conc)
  #return(forggplot_perc_1)
}


pie_chart <- function(df, main, labels = NULL, condition = NULL) {
  
  # convert the data into percentages. group by conditional variable if needed
  df <- group_by_(df, .dots = c(condition, main)) %>%
    summarise(counts = n()) %>%
    mutate(perc = counts / sum(counts)) %>%
    arrange(desc(perc)) %>%
    mutate(label_pos = cumsum(perc) - perc / 2,
           perc_text = paste0(round(perc * 100), "%", "\n","(",counts, ")"))
  
  # reorder the category factor levels to order the legend
  df[[main]] <- factor(df[[main]], levels = unique(df[[main]]))
  
  # if labels haven't been specified, use what's already there
  if (is.null(labels)) labels <- as.character(df[[main]])
  
  p <- ggplot(data = df, aes_string(x = factor(1), y = "perc", fill = main)) +
    
    # make stacked bar chart with black border
    geom_bar(stat = "identity", color = "black", width = 1) +
    
    # add the percents to the interior of the chart
    geom_text(aes(x = 1.25, y = label_pos, label = perc_text), size = 4) +
    
    # add the category labels to the chart
    # increase x / play with label strings if labels aren't pretty
    geom_text(aes(x = 1.82, y = label_pos, label = labels), size = 4) +
    
    # convert to polar coordinates
    coord_polar(theta = "y") +
    
    # formatting
    scale_y_continuous(breaks = NULL) +
    scale_fill_discrete(name = "", labels = unique(labels)) +
    theme(text = element_text(size = 12),
          axis.ticks = element_blank(),
          axis.text = element_blank(),
          axis.title = element_blank())
  
  # facet wrap if that's happening
  if (!is.null(condition)) p <- p + facet_wrap(condition)
  
  return(p)
}

```

```{r conditional_difftpbtm,echo = FALSE, eval = show_text}

if(params$sigmodin != 'sigmoid'){
     plot.new()
      legend('topleft', c("Linear fit applied, no sigmoidal plots available"),bty = 'n')
    }else{
    if(params$datype == 'intensity'){
        data_merged_2 <- params$data2
        conc<- params$concen
        pred.names <- paste0('predX',1:(params$chans -1))
        final.Names <- paste0('rep1_C',0:(params$chans - 2))
        
        topperc<-30 #difference in % between top and bottom
        # data_merged_2 <- dataMerge2()
        diffinter<- data_merged_2[(data_merged_2$predX1 -data_merged_2[,paste("predX",(params$chans-1),sep = "")]) > topperc & data_merged_2$predX1 <= 100, ]
        
        
        if(nrow(diffinter)>0){
          Diff_Top_bottom_pred<-shape_for_ggplot_pred(diffinter,log2(conc),pred.names)
          Diff_Top_bottom_perc<-shape_for_ggplot_perc(diffinter,log2(conc),final.Names)
          what<-c("(Top - Bottom) >")
          
          Diff_Top_bottom<-ggplot()+
            geom_line(data = Diff_Top_bottom_pred, aes(x=x,y=value, colour=factor(Diff_Top_bottom_pred$GeneID)), size = 1) +
            geom_point(data = Diff_Top_bottom_perc, aes(x=x,y=value, colour=Diff_Top_bottom_perc$GeneID)) +
            labs(title=paste(what,topperc,sep=""))
          
          
        }else{
          Diff_Top_bottom<-ggplot()+
            labs(title=paste("No significant Top-Bottom >" ,topperc,"%","\n","has been found", sep=""))
        }
        
        print(Diff_Top_bottom)
    } else{
        conc<- params$concen
    pred.names <- params$sigPred
    final.Names <- params$finNam
    
    topperc<-30 #difference in % between top and bottom
    data_merged_2 <- params$data2
    diffinter<- data_merged_2[(data_merged_2$predX1 -data_merged_2[,paste("predX",params$chans,sep = "")]) > topperc & data_merged_2$predX1 <= 100, ]
    
    
    
    
    if(nrow(diffinter)>0){
      Diff_Top_bottom_pred<-shape_for_ggplot_pred(diffinter,log2(conc),pred.names)
      Diff_Top_bottom_perc<-shape_for_ggplot_perc(diffinter,log2(conc),final.Names)
      what<-c("(Top - Bottom) >")
      
      Diff_Top_bottom<-ggplot()+
        geom_line(data = Diff_Top_bottom_pred, aes(x=x,y=value, colour=factor(Diff_Top_bottom_pred$GeneID)), size = 1) +
        geom_point(data = Diff_Top_bottom_perc, aes(x=x,y=value, colour=Diff_Top_bottom_perc$GeneID)) +
        labs(title=paste(what,topperc,sep=""))
      
      
    }else{
      Diff_Top_bottom<-ggplot()+
        labs(title=paste("No significant Top-Bottom >" ,topperc,"%","\n","has been found", sep=""))
    }
      }
    
    
    print(Diff_Top_bottom)
    }
```

```{r conditional_slo,echo = FALSE, eval = show_text}

    if(params$sigmodin != 'sigmoid'){
      plot.new()
      legend('topleft', c("Linear fit applied, no sigmoidal plots available"),bty = 'n')
    }else{
      if(params$datype == 'intensity'){
         top<-15 #max prot to plot
        
        conc<- params$concen
        pred.names <- paste0('predX',1:(params$chans -1))
        final.Names <- paste0('rep1_C',0:(params$chans - 2))
        
        data_merged_2 <- params$data2
        
        #Here make the subselections for using the ggplot functions SLOPE
        slope<-na.omit(data_merged_2[data_merged_2$SlopePval<0.05 ,])
        slope_ordered<-na.omit(slope[order(slope$SlopePval, decreasing = F),][1:top,])
        if(nrow(slope_ordered)>0){
          slope_pred<-shape_for_ggplot_pred(slope_ordered,log10(conc),pred.names)
          slope_perc<- shape_for_ggplot_perc(slope_ordered,log10(conc),final.Names)
          what<-c("Slope (p.val) ")
          Slope_pl<-ggplot()+
            geom_line(data = slope_pred, aes(x=x,y=value, colour=factor(slope_pred$GeneID)), size = 1) +
            geom_point(data = slope_perc, aes(x=x,y=value,colour=slope_perc$GeneID))+
            labs(title=paste(what,"Top",top,sep=""))
          
        }else{Slope_pl<-ggplot()+
          labs(title="No significant Sigmoidal Slope has been found")
        }
        print(Slope_pl)
      }else{
        top<-15 #max prot to plot

    #Here make the subselections for using the ggplot functions SLOPE
    slope<-na.omit(data_merged_2[data_merged_2$SlopePval<0.05 ,])
    slope_ordered<-na.omit(slope[order(slope$SlopePval, decreasing = F),][1:top,])
    if(nrow(slope_ordered)>0){
      slope_pred<-shape_for_ggplot_pred(slope_ordered,log10(conc),pred.names)
      slope_perc<- shape_for_ggplot_perc(slope_ordered,log10(conc),final.Names)
      what<-c("Slope (p.val) ")
      Slope_pl<-ggplot()+
        geom_line(data = slope_pred, aes(x=x,y=value, colour=factor(slope_pred$GeneID)), size = 1) +
        geom_point(data = slope_perc, aes(x=x,y=value,colour=slope_perc$GeneID))+
        labs(title=paste(what,"Top",top,sep=""))
      
    }else{Slope_pl<-ggplot()+
      labs(title="No significant Sigmoidal Slope has been found")
    }
    print(Slope_pl)
        
      }
      
    
    }
```

```{r conditional_EC50,echo = FALSE, eval = show_text}
 if(params$sigmodin != 'sigmoid'){
      plot.new()
      legend('topleft', c("Linear fit applied, no sigmoidal plots available"),bty = 'n')
    }else{
      
      if(params$datype == 'intensity'){
        
        pred.names <- paste0('predX',1:(params$chans -1))
        final.Names <- paste0('rep1_C',0:(params$chans - 2))
        
        top<-15 #max prot to plot
        
        data_merged_2 <- params$data2
        
        # EC50<-na.omit(data_merged_2[data_merged_2$EC50Err < as.numeric(summary(data_merged_2$EC50Err)[5]) & data_merged_2$EC50Pval<0.05 & data_merged_2$predX1-data_merged_2$predX9 >0 & data_merged_2$predX1 <= 100,])
        EC50 <- data.frame(na.omit(data_merged_2[data_merged_2$EC50Err < as.numeric(summary(data_merged_2$EC50Err)[5]) & data_merged_2$EC50Pval < 0.05
                                                 & data_merged_2$predX1-data_merged_2[,paste0('predX',(params$chans - 1))] >0 & data_merged_2$predX1 <= 100,]))
        
        
        EC50_ordered<- na.omit(EC50[order(EC50$EC50Pval, decreasing = F),][1:top,])
        
        if(nrow(EC50_ordered)>0){
          EC50_pred<-shape_for_ggplot_pred(EC50_ordered,log10(conc),pred.names)
          EC50_perc<-shape_for_ggplot_perc(EC50_ordered,log10(conc),final.Names)
          what<-c("EC50 (p.val) ")
          EC50_pl<-ggplot()+
            geom_line(data = EC50_pred, aes(x=x,y=value, colour=factor(EC50_pred$GeneID)), size = 1) +
            geom_point(data = EC50_perc, aes(x=x,y=value,colour=EC50_perc$GeneID))+
            labs(title=paste(what,"Top",top,sep=""))
          print(EC50_pl)
        }else{
          EC50_pl<-ggplot()+
            labs(title="No significant EC50 has been found")
        print(EC50_pl)
        }
      }else{
        
        top<-15 #max prot to plot
    
 
    
    # EC50<-na.omit(data_merged_2[data_merged_2$EC50Err < as.numeric(summary(data_merged_2$EC50Err)[5]) & data_merged_2$EC50Pval<0.05 & data_merged_2$predX1-data_merged_2$predX9 >0 & data_merged_2$predX1 <= 100,])
    EC50 <- data.frame(na.omit(data_merged_2[data_merged_2$EC50Err < as.numeric(summary(data_merged_2$EC50Err)[5]) & data_merged_2$EC50Pval < 0.05
                                             & data_merged_2$predX1-data_merged_2[,paste0('predX',(params$chans-1))] >0 & data_merged_2$predX1 <= 100,]))
    
    
    EC50_ordered<- na.omit(EC50[order(EC50$EC50Pval, decreasing = F),][1:top,])
    
    if(nrow(EC50_ordered)>0){
      EC50_pred<-shape_for_ggplot_pred(EC50_ordered,log10(conc),pred.names)
      EC50_perc<-shape_for_ggplot_perc(EC50_ordered,log10(conc),final.Names)
      what<-c("EC50 (p.val) ")
      EC50_pl<-ggplot()+
        geom_line(data = EC50_pred, aes(x=x,y=value, colour=factor(EC50_pred$GeneID)), size = 1) +
        geom_point(data = EC50_perc, aes(x=x,y=value,colour=EC50_perc$GeneID))+
        labs(title=paste(what,"Top",top,sep=""))
    }else{
      EC50_pl<-ggplot()+
        labs(title="No significant EC50 has been found")
    }
    print(EC50_pl)
      }
    
    
    }

```

```{r conditional_siglin1,echo = FALSE, eval = FALSE}
if(params$sigmodin != 'sigmoid'){
      plot.new()
      legend('topleft', c("Linear fit applied, no sigmoidal plots available"),bty = 'n')
    }else{

    top<-15 #max prot to plot
    

    linere<-data_merged_2[data_merged_2$EC50Pval=="lm-fit:intercept.slope.quadratic" & data_merged_2$predX1 > data_merged_2$predX9 & data_merged_2$predX1 <= 100 & data_merged_2$SlopePval < 0.05,]
    
    if(nrow(linere)>0){
      lin_pred<-shape_for_ggplot_pred(linere,log10(conc),pred.names)
      lin_perc<-shape_for_ggplot_perc(linere,log10(conc),final.Names)
      what<-c("Lm model Intercept Pval< 0.05 \n (failed dose-resp.) ")
      
      Linear_pl0<-ggplot()+
        geom_line(data = lin_pred, aes(x=x,y=value, colour=factor(lin_pred$GeneID)), size = 1) +
        geom_point(data = lin_perc, aes(x=x,y=value,colour=lin_perc$GeneID))+
        labs(title=paste(what,top,sep=""))
      
      
    }else{
      Linear_pl0<-ggplot()+
        labs(title="No significant Lm Intercept has been found")
    }
    
    print(Linear_pl0)
    }

```

```{r conditional_siglin2,echo = FALSE, eval = FALSE}

 if(params$sigmodin != 'sigmoid'){
      plot.new()
      legend('topleft', c("Linear fit applied, no sigmoidal plots available"),bty = 'n')
    }else{
    
    top<-15 #max prot to plot
    
    linere<-data_merged_2[data_merged_2$EC50Pval=="lm-fit:intercept.slope.quadratic" & data_merged_2$predX1 > data_merged_2$predX9 & data_merged_2$predX1 <= 100 & data_merged_2$Lower_LimitPval < 0.05,]
    
    if(nrow(linere)>0){
      lin_pred<-shape_for_ggplot_pred(linere,log10(conc),pred.names)
      lin_perc<-shape_for_ggplot_perc(linere,log10(conc),final.Names)
      what<-c("Lm model Slope Pval< 0.05 \n (failed dose-resp.) ")
      
      Linear_pl1<-ggplot()+
        geom_line(data = lin_pred, aes(x=x,y=value, colour=factor(lin_pred$GeneID)), size = 1) +
        geom_point(data = lin_perc, aes(x=x,y=value,colour=lin_perc$GeneID))+
        labs(title=paste(what,top,sep=""))
      
      
    }else{
      Linear_pl1<-ggplot()+
        labs(title="No significant Lm slope has been found")
    }
    
    print(Linear_pl1)
    }
```

```{r conditional_siglin3,echo = FALSE, eval = FALSE}
if(params$sigmodin != 'sigmoid'){
      plot.new()
      legend('topleft', c("Linear fit applied, no sigmoidal plots available"),bty = 'n')
    }else{
    
    top<-15 #max prot to plot
    
    
    
    linere<-data_merged_2[data_merged_2$EC50Pval=="lm-fit:intercept.slope.quadratic" & data_merged_2$predX1 > data_merged_2$predX9 & data_merged_2$predX1 <= 100 & data_merged_2$Upper_LimitPval < 0.05,]
    
    if(nrow(linere)>0){
      lin_pred<-shape_for_ggplot_pred(linere,log10(conc),pred.names)
      lin_perc<-shape_for_ggplot_perc(linere,log10(conc),final.Names)
      what<-c("Lm model Quadratic Pval< 0.05 \n (failed dose-resp.) ")
      
      Linear_pl2<-ggplot()+
        geom_line(data = lin_pred, aes(x=x,y=value, colour=factor(lin_pred$GeneID)), size = 1) +
        geom_point(data = lin_perc, aes(x=x,y=value,colour=lin_perc$GeneID))+
        labs(title=paste(what,top,sep=""))
      
      
    }else{
      Linear_pl2<-ggplot()+
        labs(title="No significant Lm Quadratic has been found")
    }
    
    
    print(Linear_pl2)
    }
```

```{asis, echo=show_text}
# title try 
Some arbitrary text.

1. item
2. item

Change echo=TRUE or FALSE to display/hide this chunk.
```